Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-01-02 Submission.Rmd
updating documents for submission to work and occupations
linked figures

csl               : "apa7.csl"
#documentclass     : "apa7" #interact
classoption       : "man"
output            : papaja::apa6_pdf

@@

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures 1 and 2 present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure 1 presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure 2 presents the characteristics with the greatest amount of *disagreement* across workers. The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).

 [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures 1 and 2  presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).

In addition to highlighting extremely agreed- or disagreed-upon items, Figure 3 presents our standard deviation indices across all rated items. Here, the Figure 1 discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

@@

Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).  First exploring the right side of Figure 4, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control). As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.

Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure 4. The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for Participation was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for Autonomy was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for Team Cohesion was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`). Statistical significance was less than .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories. In fact, the means were nearly identical for resource and challenge ratings for all for categories. The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.

Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure 4). The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F` ($\eta^2$ was `r report1$ANOVA$pes`). The effect for Physical Environment was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`). The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`). The effect for Emotional Demands was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for Recipient Contact was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`). The effect for Work Pressure was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a *resource* (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the left hand side of Figure 4. In other words, demands are viewed as resources. In sum, these results provide some support for RQ 1 and 2.

>>>>

csl               : "apa7.csl"
#documentclass     : "apa7" #interact
classoption       : "man"
#output            : "word_document"
output            : papaja::apa6_pdf

@@

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers. The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`). However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).

 [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items. Here, the Figure \@ref(fig:combinegraphs) discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01). In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.

@@

Figure \@ref(fig:scalelevelgraphs) presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).  First exploring the right side of Figure \@ref(fig:scalelevelgraphs), there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control). As described above, the left side of Figure \@ref(fig:scalelevelgraphs) shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.

Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \@ref(fig:scalelevelgraphs). The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for Participation was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for Autonomy was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for Team Cohesion was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`). Statistical significance was less than .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure \@ref(fig:scalelevelgraphs)). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories. In fact, the means were nearly identical for resource and challenge ratings for all for categories. The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.

Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure \@ref(fig:scalelevelgraphs)). The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F` ($\eta^2$ was `r report1$ANOVA$pes`). The effect for Physical Environment was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`). The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`). The effect for Emotional Demands was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for Recipient Contact was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`). The effect for Work Pressure was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a *resource* (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the left hand side of Figure \@ref(fig:scalelevelgraphs). In other words, demands are viewed as resources. In sum, these results provide some support for RQ 1 and 2.

### 2024-01-02 Submission.tex
linked figures

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures 1 and 2 present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures 1 and 2 presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure 1 presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure 2 presents the characteristics with the greatest amount of \emph{disagreement} across workers. The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).

In addition to highlighting extremely agreed- or disagreed-upon items, Figure 3 presents our standard deviation indices across all rated items. Here, the Figure 1 discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.

@@

Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element). First exploring the right side of Figure 4, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control). As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.

Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure 4. The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
The effect for Participation was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
The effect for Autonomy was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
The effect for Team Cohesion was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60). Statistical significance was less than .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories. In fact, the means were nearly identical for resource and challenge ratings for all for categories. The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.

Next, repeated-measures ANOVAs were also run for the group of literature-implicated \emph{demands} (see the left hand side of Figure 4). The effect for Overwork was \(F_{(2, 1134)}\) = 17.71 (\(\eta^2\) was 0.03). The effect for Physical Environment was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17). The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13). The effect for Emotional Demands was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
The effect for Recipient Contact was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65). The effect for Work Pressure was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a \emph{resource} (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the left hand side of Figure 4. In other words, demands are viewed as resources. In sum, these results provide some support for RQ 1 and 2.

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources. We explore this hypothesis first at the job characteristic level before presenting a broader perspective. Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources. The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency. Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers. The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86). However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).

In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items. Here, the Figure \ref{fig:combinegraphs} discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram). Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement. This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions. A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01). In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.

@@

Figure \ref{fig:scalelevelgraphs} presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element). First exploring the right side of Figure \ref{fig:scalelevelgraphs}, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control). As described above, the left side of Figure \ref{fig:scalelevelgraphs} shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.

Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \ref{fig:scalelevelgraphs}. The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
The effect for Participation was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
The effect for Autonomy was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
The effect for Team Cohesion was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60). Statistical significance was less than .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure \ref{fig:scalelevelgraphs}). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories. In fact, the means were nearly identical for resource and challenge ratings for all for categories. The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.

Next, repeated-measures ANOVAs were also run for the group of literature-implicated \emph{demands} (see the left hand side of Figure \ref{fig:scalelevelgraphs}). The effect for Overwork was \(F_{(2, 1134)}\) = 17.71 (\(\eta^2\) was 0.03). The effect for Physical Environment was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17). The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13). The effect for Emotional Demands was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
The effect for Recipient Contact was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65). The effect for Work Pressure was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56). In all cases, statistical significance was less then .001. However, the findings revealed that what the literature implicates as a demand was actually evaluated as a \emph{resource} (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a demand constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance. See the pattern of white resource bars on the left hand side of Figure \ref{fig:scalelevelgraphs}. In other words, demands are viewed as resources. In sum, these results provide some support for RQ 1 and 2.
